Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-13 ms.tex
removed f1 Lambert figure, added 100-217 GHz emission prediction figure and wrote corresponding discussion text

\begin{figure}
\begin{center}
\epsfig{file=f1_lambert.eps, width=3.3in}
\caption{\label{fig:f1lambert} The results of our low-resolution fit with $f_1$
allowed to vary, shown in Lambert projection to highlight the salient features 
near the north Galactic pole.}
\end{center}
\end{figure}

The resulting full-sky map of $f_1$ is shown in Figure \ref{fig:f1}. Some of 
the most striking features occur near the north Galactic pole, and to 
highlight these regions of unusually high $f_1$, we display the northern
Galactic hemisphere in Lambert projection in Figure \ref{fig:f1lambert}.

@@

% compare 100-217 GHz predictions using my model versus Planck Collaboration
% single-MBB model

@@

%end section saying that the predictions accessible through our data 
% release should be investigated/tested/swapped in by people doing
% B-mode stuff

%striping in IRAS/IRIS versus in SFD IRAS ... planck dust map obvious striping
%%%An important difference between our maps and those of \cite{planckdust} is 
%%%our 
%%%use of SFD \verb|i100| instead of IRIS 100$\mu$m \citep{IRIS}. Residual 
%%%\IRAS~striping at levels higher than that remaining in SFD \verb|i100| is 
%%%clearly visible in the \cite{planckdust} maps.

%we actually have 6.1' arcminute resolution
%%%It is true that we have smoothed the input intensity maps for this study 
%%%to $6.1'$ FWHM, which is nominally lower resolution than the $5'$ 
%%%\cite{planckdust} maps. However, as is apparent from figure 
%%%\ref{fig:comparison}, the fact that \cite{planckdust} modeled $\beta$ at 
%%%$0.5^{\circ}$ resolution has effectively blurred their dust temperature map.

>>>>

%%%\begin{figure}
%%%\begin{center}
%%%\epsfig{file=f1_lambert.eps, width=3.3in}
%%%\caption{\label{fig:f1lambert} The results of our low-resolution fit with $f_1$
%%%allowed to vary, shown in Lambert projection to highlight the salient features 
%%%near the north Galactic pole.}
%%%\end{center}
%%%\end{figure}

The resulting full-sky map of $f_1$ is shown in Figure \ref{fig:f1}. Some of 
the most striking features occur near the north Galactic pole, and to 
highlight these regions of unusually high $f_1$, we display the northern
Galactic hemisphere in Lambert projection in Figure \ref{fig:f1}.

@@

\begin{figure*}
\begin{center}
\epsfig{file=compare_lofreq.eps, width=6.6in}
\caption{\label{fig:lofreq} Comparison of low-frequency thermal dust emission 
predictions.}
\end{center}
\end{figure*}

To assess the accuracy of low-frequency emission predictions, we compare
the \PLANCK~HFI map at each of 100, 143, 217 GHz to the corresponding 
single-MBB and two-component predictions, with all maps smoothed to 
$1^{\circ}$ FWHM and binned down to $N_{side}=64$. We restrict to the 
same set of pixels used for the goodness-of-fit analysis of 
$\S$\ref{sec:hier}, with $|b|>30^{\circ}$ and $|\beta|>30^{\circ}$, also 
avoiding molecular emission, the SMICA inpainting mask, and compact sources. We
then perform a linear fit between the \PLANCK~observed emission and the 
predicted emission at each frequency and for each emission model. For these
fits, we consider the predicted emission to be the independent variable, 
since it has higher S/N than the observations, especially at 100 and 143 GHz.
We also assign pixel weights proportional to the predicted emission, so that
the best-fit lines faithfully capture the linear trend exhibited 
without being biased by the large number of very low S/N pixels with minimal 
emission. Scatter plots between the predicted and observed emission are shown 
in Figure \ref{fig:lofreq}. The best-fit lines are overplotted and their 
equations are given in the top left corner of each subplot.

All of the best-fit offsets, in both the single-MBB and two-component cases,
are within the uncertainties quoted in Table \ref{table:offs}. On the other 
hand, Figure \ref{fig:lofreq} shows that the \cite{planckdust} single-MBB 
predictions yield slopes substantially different from unity: 1.079 at 217 GHz, 
1.126 at 143 GHz, and 1.188 at 100 GHz. The fact that the slopes are larger 
than unity indicates that the \cite{planckdust} predictions are systematically 
low. The systematic underprediction evidently become gradually more severe as 
lower frequencies are considered, with a 7.9\% underprediction at 217 GHz, a 
12.6\% underprediction at 143 GHz and an 18.8\% underprediction at 100 GHz.

For the case of the two-component model, we perform full-resolution 217-3000 
GHz fits using the \PLANCK+DIRBE favored global parameters (Table 
\ref{tab:global}, model 2), then smooth to $1^{\circ}$ FWHM and bin down to 
$N_{side}=64$ before predicting the 100-217 GHz emission. The bottom row of
Figure 14 shows that each of the best-fit lines is very similar to the 
corresponding red line which represents a perfect match between predicted and 
observed emission. More quantitatively, the two-component slopes are all within
2.2\% of unity: 0.978 at 217 GHz, 0.986 at 143 GHz and 1.022 at 100 GHz. 
We note that at 217 GHz, the good agreement is in some sense predetermined by 
the fact that \PLANCK~217 GHz has been included in our two-component MCMC fits.
On the other hand, the 143 and 100 GHz predictions are truly based on 
extrapolation.

% mention imprint of Planck team's half-degree on low-freq extrapolation ?

@@

%%%It is true that we have smoothed the input intensity maps for this study 
%%%to $6.1'$ FWHM, which is nominally lower resolution than the $5'$ 
%%%\cite{planckdust} maps. However, as is apparent from figure 
%%%\ref{fig:comparison}, the fact that \cite{planckdust} modeled $\beta$ at 
%%%$0.5^{\circ}$ resolution has effectively blurred their dust temperature map.
